SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-25 scipy-1.0/paper.tex
Revised / condensed based on feedback in manuscript PR 37.

>>>>

We now provide the cumulative distribution function (using the Fortran code by
Alan Genz) of the multivariate normal distribution, \\\texttt{scipy.stats.multivariate\_normal},
via the newly associated \texttt{logcdf} and \texttt{cdf} methods. Other key recent distributions 
added to \texttt{scipy.stats} include the histogram-based
distribution in \texttt{scipy.stats.rv\_histogram} and the multinomial
distribution in \texttt{scipy.stats.multinomial} (used, for example, in natural
language processing\cite{Griffiths5228}). \texttt{multinomial} is the first and so 
far the only multivariate discrete distribution available in SciPy.

From a design standpoint, many functions in \texttt{scipy.stats} now support
a \texttt{nan\_policy} keyword to allow user-level control over the algorithmic
decision to propagate, omit, or raise an error in the case that \texttt{NaN}
values are encountered. Much of the functionality offered by
\texttt{scipy.stats} for drawing random variates now accepts a
\texttt{random\_state} parameter, which is either a \texttt{numpy.random.RandomState}
object or an integer used to generate such an object, to provide fine-grained
user-level control over the random state of a workflow.
